\section{Text-Adventure}

\subsection{Getting in the building}
The company "Notbot Sudios" is located on Lindenallee, however the main entrance is no possible way to get into the building, since my task is to go unnoticed. I checked out the area around the building and at the south of the building I could find another entrance. This entrance was for deliveries and was therefore secured with a locked gate. Luckily I had my lockpicking-set with me, and the lock "SuperSecure79244" was really easy to pick.

The stock rooms were automatically locked, and should detect if someone came from the entry or from inside. By visiting each room it could be tricked, and I managed to get into the main hall with the staircase.

\subsection{Checking out the basement}
In the basement I immediately noticed the server room, however it was locked securely with a PIN-Code. I thought maybe I can find out the code somewhere in the building, so I first wanted to check out offices in case someone wrote down the number. In another room in the west was a bunch of tools that were lying around. Those tools should be locked up too, since I did depend on those tools, to get more informations. And in the room on the west side was an overall, which had a employee card in one of its pocket.

\subsection{Checking the offices}
On the first floor I checked out all offices, and 4 were open. In the office 172 I found a key ring which I thought might be useful. The key ring was in a locked drawer, but with the screwdriver from the basement it was not a big deal to open it. In the room 845 I found a construction helmet, which I thought was rather useless. The second and third floor were closed off, but in the fourth I had luck again. One office was open, which lead to two other rooms. \\

In the second room was a plugged in computer, and when I checked it out I saw that the user be093 was still logged in. I noticed an e-mail about the meeting point the exchange the manuscript. The following room had a paper note in the drawer, which said "Huygens 175424932". At this point I wasn't sure what it referred to, but I thought it might be a pin for something. \\

Left of that room was the copy room, and I already thought employees might have forgotten important documents here. In the paper bin was a casting list for the new movie "Wahnsinn 21.1". And in the copier itself was a forgotten document, which contained parts of the manuscript for "Jo oder Helen". Employees were really sloppy and left a lot of documents lying around.\\

\subsection{Getting into Huygens office}
In the 5. floor I found the secretary of Dr. Christiaan Huygens, and east of it was his office, which was locked with a pin-code. I took a chance with the paper note I found in a drawer and got into his office. It looked rather like a storage room, and in a cupboard I found a box which said "Alte Zutrittskarten, Projekt K8" and had a note with "TODO: Loeschen vor Wiederverwendung!". Inside was a chipcard with a serialnumber. Since it was not deleted yet, I also took it because it lead to more.

\subsection{Getting to the storage server}
The storage server room was located on the west side of the basement, and because I couldn't find any code I tried to find another way to get in there. So I went into the room south of it, which was the electrical controller room. Some of the cables there seemed to be going down underneath a double-floor. I opened it with a vacuum lifting device which I found in the basement room in the east. It was a really small vent, and looked a bit dangerouse, but with the helmet I found in one of the offices it should work. So I grapped the helmet, went into the vent, went north and with the key ring from office 172 I could open the server rack. There I saw a note with the storage size, the serial number and the ip address. 
